BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-09 evaluation.tex
Layout Fixed

\begin{itemize}
\item \textbf{Collection of system information}
	   \begin{itemize}
	   \item \texttt{Systeminfo.} It outputs a summary of OS-environment parameters. 
	   \item \texttt{System File Checker (SFC).} It scans for corruptions in system files.
	   \item \texttt{Check Disk}. It checks the disks' integrity.
	   \item \texttt{IPConfig}. It displays TCP/IP network configuration values.
	   \item \texttt{Netstat}. It can show active TCP connections as well as TCP and UDP ports on which the computer is listening.
	   \item \texttt{Driver Query}. It presents the list of installed drivers and their properties.
	   \item \texttt{Windows Assessment Tools (WinSAT).} It  measures a number of performance characteristics and reports them.
	   \item \texttt{Powercfg.} It enables to search for common energy-efficiency problems. 
	   \end{itemize}
\item \textbf{Compression programs}
		\begin{itemize}
		\item \texttt{7zip.} Its default output extension is \texttt{.7z}.
		\item \texttt{IZArc.} Its default output extension is \texttt{.zip}.
		\item \texttt{WinRar.} Its default output extension is \texttt{.rar}.
		\end{itemize}
\item \textbf{Encryption Utilities}
		\begin{itemize}
		\item \texttt{Cipher.} It uses Encrypting File System (ESF), based on DESX. 
		\item \texttt{OpenSSL.} It was configured to employ 256-bit CBC AES.
		\item \texttt{Crypt.} It adopts RC2 block encryption.
		\end{itemize}
\item \textbf{Hashing Utilities}
		\begin{itemize}
		\item \texttt{File Checksum Integrity Verifier (FCIV).} It was set to use both MD5 and SHA1.
		\item \texttt{TurboSFV.} It was configured to adopt SHA3-224. 
		\end{itemize}
\end{itemize}

@@

In light of this, to actually quantify the run-time overhead we decided to adopt the following metric:

\begin{align*}
\text{Overhead per Event} = \frac{T_{instrumented} - T_{native}}{Events}
\end{align*}

@@

@@

Another popular Windows API for debug detection is \texttt{CheckRemoteDebuggerPresent}, which determines if the specified process is being debugged by a "remote" debugger, i.e., a debugger residing in parallel and different process. Its second argument is a pointer to a boolean, which is set to true if the provided process is being debugged, or false otherwise. Al-Khaser also adopts this API, and, again, BlueTracer correctly logged its invocation (\textit{Listing 4.2}). In addition, it is worth noting that the output value for the second argument (\texttt{arg 1}) is 
false (\texttt{0x0}), thus showing once more that a debugger was not discovered.

@@

@@

\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={Log entry relative to \texttt{WaitForSingleObject}},captionpos=b]
~~3160~~ 50077 kernel32.dll!WaitForSingleObject
50077 	arg 0: 0x204 (name=hHandle, type=DWORD, size=0x4)
50077 	arg 1: 0x493e0 (name=dwMilliseconds, type=DWORD, size=0x4)
50077    executed kernel32.dll!WaitForSingleObject =>
50077 	retval: 0x102 (name=Return value, type=DWORD, size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

@@

\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={Log entry relative to \texttt{RegOpenKeyExW} },captionpos=b]
~~3160~~ 30134 ADVAPI32.dll!RegOpenKeyExW
30134 	arg 0: 0x80000002 (name=hKey, type=DWORD, size=0x4)
30134 	arg 1: HARDWARE\ACPI\DSDT\VBOX__ (name=lpSubKey, type=wchar_t*, size=0x2)
30134 	arg 2: 0x0 (name=ulOptions, type=DWORD, size=0x4)
30134 	arg 3: 0x20019 (name=samDesired, type=DWORD, size=0x4)
30134 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
~~3160~~ 30135 kernel32.dll!RegOpenKeyExW
30135 	arg 0: 0x80000002 (name=hKey, type=DWORD, size=0x4)
30135 	arg 1: HARDWARE\ACPI\DSDT\VBOX__ (name=lpSubKey, type=wchar_t*, size=0x2)
30135 	arg 2: 0x0 (name=ulOptions, type=DWORD, size=0x4)
30135 	arg 3: 0x20019 (name=samDesired, type=DWORD, size=0x4)
30135 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
30135    executed kernel32.dll!RegOpenKeyExW =>
30135 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
30135 	retval: 0x2 (name=Return value, type=(long/int), size=0x4))
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

In addition to Windows registry artifacts, there are also many file system artifacts which can be checked in order to uncover the presence of a virtualized environment. Typically, specific files are searched. Al-Khaser, for instance, looks for a number of files, one of which is the \texttt{VboxMouse.sys} driver of Virtualbox. Once more, BlueTracer was able to trace these file-searching events, including the ones relative to \texttt{VboxMouse.sys} (\textit{Listing 4.9}). The \texttt{GetFileAttributesW} API, as the name suggests, is typically employed to obtain file attributes for the specified file. From \textit{Listing 4.9} it can be seen that the API returns -1, since the requested file was not found. Therefore, even in this situation, BlueTracer was also undetected.

\vspace{1cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={ Log portion relative to the search for \texttt{VboxMouse.sys} search},captionpos=b]
~~3160~~ 24979 kernel32.dll!GetFileAttributesW
24979 	arg 0: C:\Windows\system32\drivers\VBoxMouse.sys
 (name=lpFileName, type=wchar_t*, size=0x2)
~~3160~~ 24980 KERNELBASE.dll!GetFileAttributesW
24980 	arg 0: C:\Windows\system32\drivers\VBoxMouse.sys
 (name=lpFileName, type=wchar_t*, size=0x2)
24980    executed KERNELBASE.dll!GetFileAttributesW =>
24980 	retval: 0xffffffff (name=Return value, type=DWORD, size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

@@

A virtualized environment can be also discovered by looking for specific windows. The \texttt{FindWindow} API returns an handle of a window belonging to a specific class or having the specified name. This API can be exploited to check for the presence of a window associated to a virtualization program. A typical example of this trick, which is implemented by Al-Khaser, is searching for a window named "VBoxTrayToolWnd", as the presence of such window indicates that VirtualBox is being utilized. BlueTracer also detected this check (\textit{Listing 4.10}). As the reader can see, the return value is \texttt{null}, meaning that the window was not found and that BlueTracer did not reveal its presence.

@@

@@

Lastly, anti-analysis checks are aimed at detecting the existence of processes belonging to popular analysis tools. One of such tools is Process Monitor (\texttt{procmon.exe}), which is an advanced Windows monitoring tool that shows real-time file system, registry and process/thread activity \cite{procmon}. Al-Khaser looks for the processes of many analysis tools, including Process Monitor. Again, BlueTracer was also able to successfully log anti-analysis events, even the ones directed at uncovering the presence of Process Monitor (\textit{Listing 4.11}). From the listing below, it can be seen that the course of action adopted by Al-Khaser is quite straightforward. It first takes a snapshot of all the processes in the system with \texttt{CreateToolhelp32Snapshot}. Then, for each process in the snapshot, it retrieves the corresponding name, through the use of \texttt{Process32FirstW} at the beginning and \texttt{Process32NextW} afterwards, and compares it with \texttt{procmon.exe} via \texttt{StrCmpIW}.

\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={\texttt{procmon.exe} search},captionpos=b]
~~3160~~ 53940 kernel32.dll!CreateToolhelp32Snapshot
53940 	arg 0: 0x2 (name=dwFlags, type=DWORD, size=0x4)
53940 	arg 1: 0x0 (name=th32ProcessID, type=DWORD, size=0x4)
53940    executed kernel32.dll!CreateToolhelp32Snapshot =>
53940 	retval: 0x1fc (name=Return value, type=DWORD, size=0x4)
~~3160~~ 53941 kernel32.dll!Process32FirstW
53941 	arg 0: 0x1fc (name=hSnapshot, type=DWORD, size=0x4)
53941 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53941    executed kernel32.dll!Process32FirstW =>
53941 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53941 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53942 SHLWAPI.dll!StrCmpIW
53942 	arg 0: [System Process] (name=psz1, type=wchar_t*, size=0x2)
53942 	arg 1: procmon.exe (name=psz2, type=wchar_t*, size=0x2)
53942    executed SHLWAPI.dll!StrCmpIW =>
53942 	retval: 0xffffffff (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53943 kernel32.dll!Process32NextW
53943 	arg 0: 0x1fc (name=hSnapshot, type=DWORD, size=0x4)
53943 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53943    executed kernel32.dll!Process32NextW =>
53943 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53943 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53944 SHLWAPI.dll!StrCmpIW
53944 	arg 0: System (name=psz1, type=wchar_t*, size=0x2)
53944 	arg 1: procmon.exe (name=psz2, type=wchar_t*, size=0x2)
53944    executed SHLWAPI.dll!StrCmpIW =>
53944 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

>>>>

\begin{itemize}
\item \textbf{Collection of system information}
	   \begin{itemize}
	   \item \texttt{Systeminfo.} It outputs a summary of OS-environment parameters. 
	   \item \texttt{System File Checker (SFC).} It scans for corruptions in system files.
	   \item \texttt{Check Disk}. It checks the disks' integrity.
	   \item \texttt{IPConfig}. It displays TCP/IP network configuration values.
	   \item \texttt{Netstat}. It can show active TCP connections as well as TCP and UDP ports on which the computer is listening.
	   \item \texttt{Driver Query}. It presents the list of installed drivers and their properties.
	   \item \texttt{Windows Assessment Tools (WinSAT).} It  measures a number of performance characteristics and reports them.
	   \item \texttt{Powercfg.} It enables to search for common energy-efficiency problems. 
	   \end{itemize}
\item \textbf{Compression programs}
		\begin{itemize}
		\item \texttt{7zip.} Its default output extension is \texttt{.7z}.
		\item \texttt{IZArc.} Its default output extension is \texttt{.zip}.
		\item \texttt{WinRar.} Its default output extension is \texttt{.rar}.
		\end{itemize}
\item \textbf{Encryption Utilities}
		\begin{itemize}
		\item \texttt{Cipher.} It uses Encrypting File System (ESF), based on DESX. 
		\item \texttt{OpenSSL.} It was configured to employ 256-bit CBC AES.
		\item \texttt{Crypt.} It adopts RC2 block encryption.
		\end{itemize}
\vspace{2cm}
\item \textbf{Hashing Utilities}
		\begin{itemize}
		\item \texttt{File Checksum Integrity Verifier (FCIV).} It was set to use both MD5 and SHA1.
		\item \texttt{TurboSFV.} It was configured to adopt SHA3-224. 
		\end{itemize}
\end{itemize}

@@

In light of this, to actually quantify the run-time overhead we decided to adopt the following metric:
\vspace{-0.1cm}
\begin{align*}
\text{Overhead per Event} = \frac{T_{instrumented} - T_{native}}{Events}
\end{align*}

@@

%\vspace*{0.8cm}
\begin{sidewaystable}
\centering
%\begin{tabular}{cccccc}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
\begin{tabularx}{\linewidth}{*{6}{Y}}

@@

Another popular Windows API for debug detection is \texttt{CheckRemoteDebuggerPresent}, which determines if the specified process is being debugged by a "remote" debugger, i.e., a debugger residing in parallel and different process.

@@

Its second argument is a pointer to a boolean, which is set to true if the provided process is being debugged, or false otherwise. Al-Khaser also adopts this API, and, again, BlueTracer correctly logged its invocation (\textit{Listing 4.2}). In addition, it is worth noting that the output value for the second argument (\texttt{arg 1}) is 
false (\texttt{0x0}), thus showing once more that a debugger was not discovered.

@@

\vspace{1cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={Log entry relative to \texttt{WaitForSingleObject}},captionpos=b]
~~3160~~ 50077 kernel32.dll!WaitForSingleObject
50077 	arg 0: 0x204 (name=hHandle, type=DWORD, size=0x4)
50077 	arg 1: 0x493e0 (name=dwMilliseconds, type=DWORD, size=0x4)
50077    executed kernel32.dll!WaitForSingleObject =>
50077 	retval: 0x102 (name=Return value, type=DWORD, size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

@@

\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={Log entry relative to \texttt{RegOpenKeyExW} },captionpos=b]
~~3160~~ 30134 ADVAPI32.dll!RegOpenKeyExW
30134 	arg 0: 0x80000002 (name=hKey, type=DWORD, size=0x4)
30134 	arg 1: HARDWARE\ACPI\DSDT\VBOX__ (name=lpSubKey, type=wchar_t*, size=0x2)
30134 	arg 2: 0x0 (name=ulOptions, type=DWORD, size=0x4)
30134 	arg 3: 0x20019 (name=samDesired, type=DWORD, size=0x4)
30134 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
~~3160~~ 30135 kernel32.dll!RegOpenKeyExW
30135 	arg 0: 0x80000002 (name=hKey, type=DWORD, size=0x4)
30135 	arg 1: HARDWARE\ACPI\DSDT\VBOX__ (name=lpSubKey, type=wchar_t*, size=0x2)
30135 	arg 2: 0x0 (name=ulOptions, type=DWORD, size=0x4)
30135 	arg 3: 0x20019 (name=samDesired, type=DWORD, size=0x4)
30135 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
30135    executed kernel32.dll!RegOpenKeyExW =>
30135 	arg 4: 0x002bf6e4 => 0x0 (name=phkResult, type=DWORD*, size=0x4)
30135 	retval: 0x2 (name=Return value, type=(long/int), size=0x4))
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}   
\vspace{1cm}
In addition to Windows registry artifacts, there are also many file system artifacts which can be checked in order to uncover the presence of a virtualized environment. Typically, specific files are searched. Al-Khaser, for instance, looks for a number of files, one of which is the \texttt{VboxMouse.sys} driver of Virtualbox. Once more, BlueTracer was able to trace these file-searching events, including the ones relative to \texttt{VboxMouse.sys} (\textit{Listing 4.9}). The \texttt{GetFileAttributesW} API, as the name suggests, is typically employed to obtain file attributes for the specified file. From \textit{Listing 4.9} it can be seen that the API returns -1, since the requested file was not found. Therefore, even in this situation, BlueTracer was also undetected.

\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={ Log portion relative to the search for \texttt{VboxMouse.sys} search},captionpos=b]
~~3160~~ 24979 kernel32.dll!GetFileAttributesW
24979 	arg 0: C:\Windows\system32\drivers\VBoxMouse.sys
 (name=lpFileName, type=wchar_t*, size=0x2)
~~3160~~ 24980 KERNELBASE.dll!GetFileAttributesW
24980 	arg 0: C:\Windows\system32\drivers\VBoxMouse.sys
 (name=lpFileName, type=wchar_t*, size=0x2)
24980    executed KERNELBASE.dll!GetFileAttributesW =>
24980 	retval: 0xffffffff (name=Return value, type=DWORD, size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

@@

A virtualized environment can be also discovered by looking for specific windows. The \texttt{FindWindow} API returns an handle of a window belonging to a specific class or having the specified name.

@@

This API can be exploited to check for the presence of a window associated to a virtualization program. A typical example of this trick, which is implemented by Al-Khaser, is searching for a window named "VBoxTrayToolWnd", as the presence of such window indicates that VirtualBox is being utilized. BlueTracer also detected this check (\textit{Listing 4.10}). As the reader can see, the return value is \texttt{null}, meaning that the window was not found and that BlueTracer did not reveal its presence.

@@

Lastly, anti-analysis checks are aimed at detecting the existence of processes belonging to popular analysis tools. One of such tools is Process Monitor (\texttt{procmon.exe}), which is an advanced Windows monitoring tool that shows real-time file system, registry and process/thread activity \cite{procmon}. Al-Khaser looks for the processes of many analysis tools, including Process Monitor. Again, BlueTracer was also able to successfully log anti-analysis events, even the ones directed at uncovering the presence of Process Monitor (\textit{Listing 4.11}). From the listing below, it can be seen that the course of action adopted by Al-Khaser is quite straightforward. It first takes a snapshot of all the processes in the system with \texttt{CreateToolhelp32Snapshot}. Then, for each process in the snapshot, it retrieves the corresponding name, through the use of \texttt{Process32FirstW} at the beginning and \texttt{Process32NextW} afterwards, and compares it with \texttt{procmon.exe} via \texttt{StrCmpIW}. 
\vspace{0.5cm}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
\begin{lstlisting}[caption={\texttt{procmon.exe} search},captionpos=b]
~~3160~~ 53940 kernel32.dll!CreateToolhelp32Snapshot
53940 	arg 0: 0x2 (name=dwFlags, type=DWORD, size=0x4)
53940 	arg 1: 0x0 (name=th32ProcessID, type=DWORD, size=0x4)
53940    executed kernel32.dll!CreateToolhelp32Snapshot =>
53940 	retval: 0x1fc (name=Return value, type=DWORD, size=0x4)
~~3160~~ 53941 kernel32.dll!Process32FirstW
53941 	arg 0: 0x1fc (name=hSnapshot, type=DWORD, size=0x4)
53941 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53941    executed kernel32.dll!Process32FirstW =>
53941 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53941 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53942 SHLWAPI.dll!StrCmpIW
53942 	arg 0: [System Process] (name=psz1, type=wchar_t*, size=0x2)
53942 	arg 1: procmon.exe (name=psz2, type=wchar_t*, size=0x2)
53942    executed SHLWAPI.dll!StrCmpIW =>
53942 	retval: 0xffffffff (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53943 kernel32.dll!Process32NextW
53943 	arg 0: 0x1fc (name=hSnapshot, type=DWORD, size=0x4)
53943 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53943    executed kernel32.dll!Process32NextW =>
53943 	arg 1: 0x002b7408 (name=lppe, type=struct*|tagPROCESSENTRY32W, size=0x1160)
53943 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
~~3160~~ 53944 SHLWAPI.dll!StrCmpIW
53944 	arg 0: System (name=psz1, type=wchar_t*, size=0x2)
53944 	arg 1: procmon.exe (name=psz2, type=wchar_t*, size=0x2)
53944    executed SHLWAPI.dll!StrCmpIW =>
53944 	retval: 0x1 (name=Return value, type=(long/int), size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}
